Update of the ozone dry deposition in the OsloCTM3 v1.0

### 2018-10-25 DryDep.tex
Finished Section 2. Needs to be read one more time before tagging and shippment to co-authors.

@@

Light in the wavelength band $(400-700)$\,\unit{nm} to which the plant chlorophyll is sensitive is called photosynthetic active radiation (PAR). In the EMEP parameterization, an integrated photon flux -- photosynthetic photon flux density (PPFD) -- is used to mimic the time lag of the opening and closing of stomata with respect to light instead of a simple day-on/night-off treatment:

@@

@@

The non-stomatal conductance for \chem{O_3} consists of two terms, one depending on vegetation type and one depending in the soil/surface. For a land surface type $N$, we can write
\begin{equation}
  G_\text{ns}^\chem{O_3}(N) = \frac{\text{SAI}(N)}{r_\text{ext}} + \frac{1}{R_\text{inc}(N) + R_\text{gs}^\chem{O_3}(N)}.
\end{equation}
$\text{SAI}(N)$ is the surface area index for vegetation type $N$, which is $\text{LAI}$ plus some value representing cuticles and others surfaces. The external leaf resistance is defined by
\begin{equation}
  r_\text{ext} = 2000\cdot F_T\,\unit{sm^{-1}}.
\end{equation}
Herein $F_T$ is a temperature correction factor for temperatures below $-1\,\unit{^\circ C}$ and $\{F_T \in \mathbb{R} | (1 \leq F_T \leq 2)\}$
\begin{equation}
  F_T = \exp{(-2\cdot(1+\theta_0))}.
\end{equation}
$\theta_0$ is the surface or 2\,\unit{m} temperature in \unit{^\circ C}. In general, $\text{SAI} \equiv \text{LAI}$ for all land types, except for: 
%
\begin{equation}
  \text{SAI} = 
  \begin{cases}
    \text{LAI}+1 & \emph{if} \quad \text{\emph{forest / wetland}},\\
    \text{LAI}\cdot 5/3.5 & \emph{if} \quad \text{\emph{cropland}, I. part of growing season},\\
    \text{LAI} + 1.5 & \emph{if} \quad \text{\emph{cropland}, II. part of growing season},\\
    0 & \emph{if} \quad \text{\emph{cropland}, winter}.
  \end{cases}
\end{equation}
%
Extending the EMEP scheme to the southern hemisphere, the used growing season for crops is defined in Table~\ref{tab:growing_season}.
\begin{table}[t]
  \caption{Definition of growing season for crops used in the OsloCTM3 in northern hemisphere (NH) and southern hemisphere (SH).}
  \begin{tabular}{lrr}
    \tophline
    & I. part & II. part \\
    & (days) & (days) \\
    \middlehline
    NH & 90--140 & 141--270 \\
    SH & 272--322 & 323--452 \\
    \bottomhline
  \end{tabular}
  %\belowtable{} % Table Footnotes
  \label{tab:growing_season}
\end{table}
%

@@

The original EMEP scheme uses fixed start of growing season (SGS) and end of growing season (EGS) at $50\,\unit{^\circ N}$ together with leapsrates ($d_\text{SGS}$, $d_\text{EGS}$, $\nabla d_\text{SGS}$, and $\nabla d_\text{EGS}$ in Supplement~S.2) to define phenology and dry deposition over agricultural areas. However this parameterization fails in a global model, therefor another latitude dependent parameterization is needed. First, we have used a parameterization as implemented in the Sparse Matrix Operational Kernel Emissions -- Biogenic Emission Inventory System (SMOKE-BEIS) model. SMOKE-BEIS has fixed values for SGS and EGS for all regions but NH mid latitudes ($23\,\unit{^\circ} < \text{lat} < 65\,\unit{^\circ}$), where it uses leapsrates of $\nabla d_\text{SGS} = 4.5$ and $\nabla d_\text{EGS} = 3.3$. This parameterization works well, if the focus of the scientific work lies on mid latitudes and North America. In Europe, however, most of northern Scandinavia has no vegetation period according to this parameterization.

In agriculture, there are differing empirical rules to estimate the SGS and EGS. The simplest assumption is that greening starts after 5 consecutive days with a daily average temperature above 5\,\unit{^\circ C} and vice versa for EGS. If, within these 5 days, the temperature drops below / rises above 5\,\unit{^\circ C}, the counters are reset. With respect to model performance, we decided to preprocess our meteorological input date using this 5\,\unit{^\circ C}-days criteria for $45\,\unit{^\circ} < \text{lat} < 85\,\unit{^\circ}$ in the NH and $35\,\unit{^\circ} < \text{lat} < 65\,\unit{^\circ}$ in the SH. In all other cases and where the 5\,\unit{^\circ C}-days criterion fails, we use the SMOKE-BEIS parameterization.

Instead of SGS and EGS, we use the derived parameters day of greening season (GDAY), which is the time elapsed starting at the SGS, and the total length of the greening season (GLEN), which is the time between EGS and SGS. Example maps of the computed GLEN are shown in Supplement~S.4.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Photosynthetic photon flux density (PPFD)}
From OpenIFS an accumulated photosynthetic active radiation (PAR) is available, but needs to be deaccumulated. Strictly speaking, since this field is already integrated over the whole spectrum, it is not the actual PAR but PPFD. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%      
\section{Evaluation}
\label{sec:eval}
For meteorological input, we use \href{https://www.ecmwf.int/en/forecasts/documentation-and-support/evolution-ifs/cycle-38r1-summary-changes}{ECMWF - OpenIFS version cy38r1nc4}. CEDS historical emission inventory is used for emissions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sensitivity tests}
\label{subsec:sens}
Include table of all sensitivity runs.
\citep[e.g., $v^\chem{O_3}_{ice/snow} = 1/10000\,\unit{cm\,s^{-1}}$,][]{ACP:Helmig2007}
dry dep velocity over water \citep{JGR:Helmig2012} Impact of ocean? Although it is a low number there is 2\/3 ocean on earth... (Think, I read this in Hardacre paper... -> Luhar)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with recent multi-model comparison}
\label{subsec:model}
Compare to \citet{ACP:Hardacre2015} as well as \citet{ACP:Luhar2017}. \citep{AE:Derwent2018} Uncertainties in surface ozone sources and sinks larger than in formulations? -> Need to read this one...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with observations}
\label{subsec:obs}
The sites used in \citet{ACP:Hardacre2015} and additional ozone zonal data from satellites and sondes (\url{http://bodekerscientific.com/}). \citep{AE:Hu2017} -> need to look into this one...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:disc}

@@

\appendix
\section{Land use and plant function types (PFT)}    %% Appendix A
\appendixfigures
\begin{figure}[t]
  \centering
  \includegraphics[width=8.3cm]{pictures/pft_categories.pdf}\\
  \includegraphics[width=8.3cm]{pictures/pft_categories_zonal.pdf}
  \caption{Plant functional types (PFT). (a) CML2 dynamic land surface 0.5x0.5\,\unit{^\circ}}
  \label{fig:pft_landsurface}
\end{figure}
\subsection{}     %% Appendix A1, A2, etc.

>>>>

  \label{eq:fphen}

@@

Light in the wavelength band $(400-700)$\,\unit{nm} to which the plant chlorophyll is sensitive is called photosynthetic active radiation (PAR). In the EMEP parameterization, an integrated photon flux is used to mimic the time lag of the opening and closing of stomata with respect to light instead of a simple day-on/night-off treatment:

@@

  \label{eq:flight}

@@

The non-stomatal conductance for \chem{O_3} consists of two terms, one depending on vegetation type and one depending in the soil/surface. For a land surface type $N$, we can write
\begin{equation}
  G_\text{ns}^\chem{O_3}(N) = \frac{\text{SAI}(N)}{r_\text{ext}} + \frac{1}{R_\text{inc}(N) + R_\text{gs}^\chem{O_3}(N)}.
  \label{eq:non-stomata-cond}
\end{equation}
$\text{SAI}(N)$ is the surface area index for vegetation type $N$, which is $\text{LAI}$ plus some value representing cuticles and others surfaces. The external leaf resistance is defined by
\begin{equation}
  r_\text{ext} = 2000\cdot F_T\,\unit{sm^{-1}}.
\end{equation}
Herein $F_T$ is a temperature correction factor for temperatures below $-1\,\unit{^\circ C}$ and $\{F_T \in \mathbb{R} | (1 \leq F_T \leq 2)\}$
\begin{equation}
  F_T = \exp{(-2\cdot(1+\theta_0))}.
\end{equation}
$\theta_0$ is the surface or 2\,\unit{m} temperature in \unit{^\circ C}. In general, $\text{SAI} \equiv \text{LAI}$ for all land types, except for: 
%
\begin{equation}
  \text{SAI} = 
  \begin{cases}
    \text{LAI}+1 & \emph{if} \quad \text{\emph{forest / wetland}},\\
    \text{LAI}\cdot 5/3.5 & \emph{if} \quad \text{\emph{cropland}, I. part of growing season},\\
    \text{LAI} + 1.5 & \emph{if} \quad \text{\emph{cropland}, II. part of growing season},\\
    0 & \emph{if} \quad \text{\emph{cropland}, winter}.
  \end{cases}
  \label{eq:SAI}
\end{equation}
%
Extending the EMEP scheme to the southern hemisphere, the used growing season for crops is defined in Table~\ref{tab:growing_season}.
\begin{table}[t]
  \caption{Definition of growing season for crops used in the OsloCTM3 in northern hemisphere (NH) and southern hemisphere (SH).}
  \begin{tabular}{lrr}
    \tophline
    & I. part & II. part \\
    & (days) & (days) \\
    \middlehline
    NH & 90--140 & 141--270 \\
    SH & 272--322 & 323--452 \\
    \bottomhline
  \end{tabular}
  %\belowtable{} % Table Footnotes
  \label{tab:growing_season}
\end{table}
%

@@

In Eqs.~(\ref{eq:non-stomata-cond}--\ref{eq:SAI}), \citet{ACP:Simpson2012} use fixed start of growing season (SGS) and end of growing season (EGS) at $50\,\unit{^\circ N}$ together with leaprates ($d_\text{SGS}$, $d_\text{EGS}$, $\nabla d_\text{SGS}$, and $\nabla d_\text{EGS}$) to define phenology and dry deposition over agricultural areas. For the growing season of crops in the computation of non-stomatal conductances, we use fixed values (Table~\ref{tab:growing_season}), while for the stomatal conductances, as shown in Eq.~(\ref{eq:fphen}), we use the SGS and EGS derived parameters: day of greening season (GDAY), the time elapsed starting at the SGS, and the total length of the greening season (GLEN), the time span between EGS and SGS. Since the eurocentric EMEP parameterization of SGS and EGS is not applicable in a global model, another latitude dependent parameterization is needed. First, we have used a parameterization as implemented in the Sparse Matrix Operational Kernel Emissions -- Biogenic Emission Inventory System (SMOKE-BEIS; \href{https://www.epa.gov/air-emissions-modeling/biogenic-emission-inventory-system-beis}{model webpage}). SMOKE-BEIS has fixed values for SGS and EGS for all regions but NH mid latitudes ($23\,\unit{^\circ} < \text{lat} < 65\,\unit{^\circ}$), where it uses leaprates of $\nabla d_\text{SGS} = 4.5$ and $\nabla d_\text{EGS} = 3.3$. As this parameterization is optimized for North America, it does not work well in Europe, e.g., most of northern Scandinavia has no allocated vegetation period.

In agriculture, there are different empirical rules to estimate the SGS and EGS. The simplest assumption is that greening starts after 5 consecutive days with a daily average temperature above 5\,\unit{^\circ C} and vice versa for EGS. Based on this rule of thumb, we have pre-processed our meteorological input data offline. If, within these 5 days, the temperature drops below / rises above 5\,\unit{^\circ C}, the counters are reset, respectively. First, we used the 5\,\unit{^\circ C}-days criteria for $45\,\unit{^\circ} < \text{lat} < 85\,\unit{^\circ}$ in the NH, but extended it also to $35\,\unit{^\circ} < \text{lat} < 65\,\unit{^\circ}$ in the SH. In all other cases and where the 5\,\unit{^\circ C}-days criteria fails, we use the SMOKE-BEIS parameterization. The described algorithm written in python 2.7 has been included as Supplement~S.4.1. An example map of the computed GLEN using the 5\,\unit{^\circ C}-days criteria in both hemispheres is shown in Fig.~\ref{fig:glen_2015_she}.
%
\begin{figure}[t]
  \includegraphics[width=8.3cm, clip, trim={0.cm 1.75cm 0.cm 1.75cm}]{pictures/GLEN_2005_she.pdf}
  \caption{Pre-processing of greening season from meteorological surface temperature fields. Shown is the total length of the greening season (GLEN) for the year 2005. The 5\,\unit{^\circ C}-days criteria has been used in both hemispheres mid--high latitudes. Ocean has been shaded to indicate that greening season will only affect land.}
  \label{fig:glen_2015_she}
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Photosynthetic photon flux density}
From OpenIFS an accumulated photosynthetic active radiation is available, but for practical use in Eq.~(\ref{eq:flight}) it needs to be deaccumulated. Since this field is already integrated over the spectrum $(400-700)\,\unit{nm}$, it is not PAR but PPFD. Therefor, we will refer to the deaccumulated field as PPFD. An example PAR for January 2nd 2005 is shown in Supplement~S.5.1. Deaccumulation of hour 3 till 21, simply means
\begin{equation}
  \text{PPFD}(t_i) = \text{PAR}(t_{i+1})-\text{PAR}(t_i).
\end{equation}
If everything was right in the OpenIFS output, we would not need to do any further processing, however the first timestep of each day has already accumulated PAR from some other date and time in addition to the actual hour 0 data (see Supplement~S.5.2), so it is impossible to accurately deaccumulate this time step. The best choice is subtracting the difference between hour 21 and 12 of the previous day (Supplement~S.5.3)
\begin{equation}
  \text{PPFD}(t=0) = \text{PAR}(t=0) - \left[\text{PAR}(t=21\,\unit{h}-1\,\unit{day})-\text{PAR}(=12\,\unit{h}-1\,\unit{day})\right].
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%      
\section{Evaluation}
\label{sec:eval}
For meteorological input, we use \href{https://www.ecmwf.int/en/forecasts/documentation-and-support/evolution-ifs/cycle-38r1-summary-changes}{ECMWF - OpenIFS version cy38r1nc4}. CEDS historical emission inventory is used for emissions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sensitivity tests}
\label{subsec:sens}
Include table of all sensitivity runs.
\citep[e.g., $v^\chem{O_3}_{ice/snow} = 1/10000\,\unit{cm\,s^{-1}}$,][]{ACP:Helmig2007}
dry dep velocity over water \citep{JGR:Helmig2012} Impact of ocean? Although it is a low number there is 2\/3 ocean on earth... (Think, I read this in Hardacre paper... -> Luhar)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with recent multi-model comparison}
\label{subsec:model}
Compare to \citet{ACP:Hardacre2015} as well as \citet{ACP:Luhar2017}. \citep{AE:Derwent2018} Uncertainties in surface ozone sources and sinks larger than in formulations? -> Need to read this one...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with observations}
\label{subsec:obs}
The sites used in \citet{ACP:Hardacre2015} and additional ozone zonal data from satellites and sondes (\url{http://bodekerscientific.com/}). \citep{AE:Hu2017} -> need to look into this one...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{sec:disc}

@@

\appendix
\section{Land use and plant function types (PFT)}    %% Appendix A
\appendixfigures
\begin{figure}[t]
  \centering
  \includegraphics[width=8.3cm]{pictures/pft_categories.pdf}\\
  \includegraphics[width=8.3cm]{pictures/pft_categories_zonal.pdf}
  \caption{Plant functional types (PFT). (a) CML2 dynamic land surface (0.5x0.5)\,\unit{^\circ}; (b) Zonal distribution of land surface types.}
  \label{fig:pft_landsurface}
\end{figure}
\subsection{}     %% Appendix A1, A2, etc.

### 2018-10-25 DryDep_supplement.tex
Finished Section 2. Needs to be read one more time before tagging and shippment to co-authors.

\subsection*{S.4 Temperature dependent greening season 2005}
\subsubsection*{S.4.1 GLEN: NH mid--high latitudes only}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight]{pictures/GLEN_2005.pdf}
\end{center}
\subsubsection*{S.4.1 GLEN: NH and SH mid--high latitudes}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight]{pictures/GLEN_2005_she.pdf}
\end{center}

\subsection*{S.5 De-accumulation of photoactive radiation (PAR) from OpenIFS: January 1st 2005}
\subsubsection*{S.5.1 Output from OpenIFS: Accumulated PAR}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight]{pictures/PAR_as_is.png}
\end{center}
\subsubsection*{S.5.2 Partly de-accumulated}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight]{pictures/PAR_partly_deaccumulated.png}
\end{center}
\subsubsection*{S.5.3 De-accumulation of hour 00}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight]{pictures/PAR_deaccumulating_00h.png}
\end{center}

>>>>

\subsection*{S.4 Temperature dependent greening season}
\subsubsection*{S.4.1 Python code snippets}
\begin{verbatim}
#----------------------------------------------------------------------------------
import numpy as np
import pandas as pd
import xarray as xr
#----------------------------------------------------------------------------------
def start_growing_season_fixed(lat, **kwargs):
    '''
    Begin of growing season parameterization adapted from SMOKE-BEIS.
    '''
    bLeap = kwargs.pop('leap', False)
    if (bLeap):
       MAY31 = 152
       NOV1  = 306
       DEC31 = 366
    else:
       MAY31 = 151
       NOV1  = 305
       DEC31 = 365

    if lat < -65:
        return((0,))
    elif lat < -23:
        return((NOV1,1))
    elif lat <= 23:
        return((1,))
    elif lat < 65:
        return(((lat-23)*4.5,))
    else:
        return((0,))
#----------------------------------------------------------------------------------
def end_growing_season_fixed(lat, **kwargs):
    '''
    End of growing season parameterization adapted from SMOKE-BEIS.
    '''
    bLeap = kwargs.pop('leap', False)
    if (bLeap):
       MAY31 = 152
       NOV1  = 306
       DEC31 = 366
    else:
       MAY31 = 151
       NOV1  = 305
       DEC31 = 365

    if lat < -65:
        return((0,))
    elif lat < -23:
        return((DEC31,MAY31))
    elif lat <= 23:
        return((DEC31,))
    elif lat < 65:
        return((DEC31-(lat-23)*3.3,))
    else:
        return((0,))
#----------------------------------------------------------------------------------
def growing_season(temperature,**kwargs):
    '''
    Agricultural rule of thumb definition of growing season:
    5 consecutive days above 5 degree Celsius 
    and vice versa for end of growing season.
    '''
    # Shift start day of evaluation.
    s_shift = kwargs.pop('s_shift',365/2)
    # Number of days that need to fulfill temperature criteria
    degree_days_crit = kwargs.pop('ddc', 5)
    # Temperature criteria
    temperature_crit = kwargs.pop('tc', 5)
    # Switch to southern hemisphere evaluation
    sh = kwargs.pop('sh', False)
    # Activate verbose
    verbose = kwargs.pop('verbose', False)
    # Counters
    count_gdd = 0
    count_days = 0
    start_gs = (0,False)
    end_gs = (0,False)

    if sh:
    # Shift the temperature by halve a year - shifted back later.
        temp = temperature.roll(time=s_shift)
    else:
        temp = temperature
    for itemp in temp:
        count_days += 1
        if not start_gs[1]:
            if itemp > temperature_crit:
                count_gdd += 1
            else:
                count_gdd = 0
            if count_gdd == degree_days_crit:
                if sh:
                    start_gs = (count_days+s_shift, True)
                else:
                    start_gs = (count_days, True)
                count_gdd = 0
        elif start_gs[1] and not end_gs[1] and count_days>s_shift:
            if itemp <= temperature_crit:
                count_gdd += 1
                if verbose:
                    print(count_days, count_gdd)
            else:
                count_gdd = 0
            if count_gdd == degree_days_crit:
                if sh:
                    end_gs = (count_days-s_shift, True)
                else:
                    end_gs = (count_days, True)
                count_gdd = 0

    return({'sgs':start_gs,'egs':end_gs})
#----------------------------------------------------------------------------------
def growing_season_stadyn(xr_temp):
    '''
    Preprocess the greening season for OsloCTM3.
    Setting using the 5deg-5days criteria and in case this fails
    or is out of the defined bounds,
    fall back to SMOKE-BEIS parameterization.
    '''
    # Fetch leap year from input data
    bLeap = False
    if xr_temp.time.size==366:
       bLeap = True
    # Use 5deg-5days criteria   
    if (xr_temp.lat > 45 and xr_temp.lat < 85):
        gs = growing_season(xr_temp)
        sgs = (gs['sgs'][0],)
        egs = (gs['egs'][0],)
        if ( not gs['sgs'][1] or not gs['egs'][1] or sgs[0]>=egs[0]):
            # Check for failing 5deg-5days criteria => Fall back to fixed
            sgs = start_growing_season_fixed(xr_temp.lat.data, leap=bLeap)
            egs = end_growing_season_fixed(xr_temp.lat.data, leap=bLeap)
    elif (xr_temp.lat < -35 and xr_temp.lat >= -65):
        gs = growing_season(xr_temp, sh=True)
        sgs = (gs['sgs'][0],1)
        egs = (xr_temp.size, gs['egs'][0])
        # Check for failing 5deg-5days criteria => Fall back to fixed
        if (not gs['sgs'][1] or not gs['egs'][1] or sgs[0]>=egs[0]):
            sgs = start_growing_season_fixed(xr_temp.lat.data, leap=bLeap)
            egs = end_growing_season_fixed(xr_temp.lat.data, leap=bLeap)
    # Use SMOKE-BEIS parameterization
    else:
        sgs = start_growing_season_fixed(xr_temp.lat.data, leap=bLeap)
        egs = end_growing_season_fixed(xr_temp.lat.data, leap=bLeap)
    # Generate GDAY and GLEN fields
    # in case no growing season has been allocated
    if (sgs[0]==egs[0]==0):
        gday = np.repeat(0,len(xr_temp.time))
        glen = 0
    # in normal cases
    else:
        # handle northern hemisphere
        if len(sgs)==1:
            gday = np.concatenate((np.repeat(0,int(sgs[0])-1),
                                   np.arange(1,int(egs[0])-int(sgs[0])+1),
                                   np.repeat(0,len(xr_temp.time)-
                                   int(egs[0])+1)))
            glen = int(egs[0])-int(sgs[0])+1
        # handle southern hemisphere
        else:
            gday = np.concatenate((np.arange(1,int(egs[1])+1)+len(xr_temp.time)
                                   -int(sgs[0])+1,
                                   np.repeat(0,int(sgs[0])-int(egs[1])),
                                   np.arange(1,len(xr_temp.time)-int(sgs[0])+1)))
            glen = len(xr_temp.time)-(int(sgs[0])-int(egs[1]))+1
    # This should not happen, but in case it does, print info.
    if not(len(gday)==len(xr_temp.time)):
        print(xr_temp, sgs, egs)
    # Output
    data_gday = xr.DataArray(gday.astype(int),[('time', xr_temp.time.data)])
    return(data_gday, (int)(glen))
#----------------------------------------------------------------------------------
\end{verbatim}
%\subsubsection*{S.4.2 GLEN: NH mid--high latitudes only}
%\appendixfigures
%\begin{center}
%  \includegraphics[height=0.4\textheight, clip, trim={0.cm 1.75cm 0.cm 1.75cm}]{pictures/GLEN_2005.pdf}
%\end{center}

\subsection*{S.5 De-accumulation of photosynthetic active radiation (PAR) from OpenIFS: January 2nd 2005}
\subsubsection*{S.5.1 Output from OpenIFS: Accumulated PAR}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.75cm 0.75cm 0.75cm 0.75cm}]{pictures/PAR_as_is.png}
\end{center}
\subsubsection*{S.5.2 Partly de-accumulated}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.75cm 0.75cm 0.75cm 0.75cm}]{pictures/PAR_partly_deaccumulated.png}
\end{center}
\subsubsection*{S.5.3 De-accumulation of hour 00}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.75cm 0.75cm 0.75cm 0.75cm}]{pictures/PAR_deaccumulating_00h.png}
\end{center}
